---
title: "Letty Tarin"
format: 
  html:
    toc: true
    toc-title: "On This Page:"
    code-fold: true
    code-tools: false
    source: false
    search: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| output: false
#| echo: false


library(tidyverse)
library(scales)
library(plotly)
library(RColorBrewer)
theme_set(theme_light())
```


## Overview

This page includes a few samples of data analysis projects I've completed over the past year. The analyses included students from all colleges, majors and school years. The employer industries include only the industries I moderate. All analyses were done in the RStudio IDE. Click the **Code** button above the figure to view the code used to create each graph.


```{r}
#| output: false
#| echo: false

march_school_year <- read_csv("~/Desktop/March/march_school_year.csv")
march_gender <- read_csv("~/Desktop/March/march_gender.csv")

my_postings <- read_csv("/Users/lt/Desktop/2025/my_employer_postings_and_applications_nov_to_feb17.csv") %>% 
mutate(job_id = as.factor(job_id),employer_name = as.factor(employer_name), industry = as.factor(industry), 
       max_salary = replace_na(max_salary, 0))


five_yrs <- last_5_years <- read_csv("~/Downloads/last 5 years.csv") %>% 
rename(date = "Postings Responded On Date") %>% 
 mutate(date = as.Date(date, "%m/%d/%Y"),
         year = year(date))



```

### March 2024

This first example includes graphs that were part of a larger analysis I completed in March 2024 that covered top industries, number of applicants by college, gender and school year. The first graph is a visualization of applicants by school year, including advanced degrees and alumni. The second graph visualizes the total applicants by gender.

```{r}
#| code-fold: true


sy_longer <- march_school_year |> 
  pivot_longer(
    cols = alumni:sophomore,
    names_to = "school_year",
    values_to = "applicants",
    values_drop_na = TRUE
  )

sy_longer |> 
  mutate(school_year = school_year |> fct_infreq() |> fct_rev()) |> 
  ggplot(aes(school_year, fill = school_year)) +
  geom_bar(show.legend = FALSE)+
  scale_color_brewer(palette = "Set1")+
  labs(
    x = "",
    y = "",
    title = "Number of Applicants by School Year",
    subtitle = "March 2024"
  )


march_longer <- march_gender |> 
  pivot_longer(
    cols = female:male,
    names_to = "gender",
    values_to = "applicants",
    values_drop_na = TRUE
  )

march_longer |> 
  drop_na(job_type) |> 
  mutate(job_type = job_type |> fct_rev()) |> 
  ggplot(aes(job_type, fill = gender)) +
  geom_bar(position = "dodge")+
  scale_color_brewer(palette = "Set1")+
  labs(x = "",
       y = "",
       fill = "Gender",
       title = "Applicants by Job Type and Gender", 
       subtitle = "March 2024")

```

```{r}
#| output: false
#| echo: false

applications <- my_postings %>% 
group_by(industry) %>%  
  summarize(total = sum(applications_count)) %>% 
  arrange(desc(total)) %>% 
  slice_head(n = 20) %>% 
  ungroup() %>% 
  mutate(industry = fct_reorder(industry, total)) 

```


### Top 20 Most Applied To
The following example was completed to explore student engagement during the end of the Fall 2024 semester and early Spring 2025 semester. It reflects the top 20 industries most applied to during this time. This includes only the industries I moderate. 
```{r}
#| code-fold: true

applications %>% 
  ggplot(aes(x = industry, y = total, fill = industry)) +
  geom_col() +
  coord_flip() +
  scale_y_continuous(labels = comma) +
  theme(legend.position = "none") +
  labs(x = "Industry",
       y = "Number of applicants",
       title = "Total Student Applicants by Industry",
       subtitle = "November 2024 to February 2025") +
  theme(legend.position = "none")




```

```{r}
#| output: false
#| echo: false



top_industries <- my_postings %>% 
 count(industry, sort = TRUE) %>% 
  slice_head(n = 20) |> 
  mutate(industry = fct_reorder(industry, n))


```

### Top 20 Employer Industries
This graph shows the number of job and internship postings by industry at the end of the Fall 2024 semester and early Spring 2025. It reflects the number of job and internship postings by industry, versus the student applications by industry as in the graph above. 

```{r}
#| code-fold: true

top_industries %>% 
  ggplot(aes(industry, n, fill = industry))+
  geom_col()+
  coord_flip()+
  scale_y_continuous(labels = comma) +
  theme(legend.position = "none")+
  labs(title = "Top Employer Industries",
       subtitle = "November 2024 to February 2025", 
       x = "Industry",
       y = "Postings count")

```

### Applications 2021-2024
Another snapshot here to see the number of student applications from 2021 to 2024.

```{r}
#| code-fold: true


five_yrs %>% 
  filter(year != 2025 & !is.na(year)) %>% 
  group_by(year) %>% 
  summarize(total = sum(applications_count),
            n = n()) %>% 
  ggplot(aes(year,total)) +
  geom_line() +
  scale_y_continuous(labels = comma) +
  labs(x = "Year",
       y = "Applications",
       title = "Total Applications from 2021 to 2024")


```