---
title: "Letty Tarin"
format: 
  html:
    toc: true
    toc-title: "On This Page:"
    code-fold: true
    code-tools: false
    source: false
    search: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| output: false
#| echo: false


library(tidyverse)
library(scales)
library(RColorBrewer)
theme_set(theme_light())
```


## Overview

Below are a few samples of analysis I've completed. All analysis was done in the RStudio IDE. Click the **Code** button above the figure to view the code used to create each graph.

```{r}
#| output: false
#| echo: false

library(tidyverse)
library(scales)
library(RColorBrewer)
theme_set(theme_light())
```

```{r}
#| output: false
#| echo: false

march_school_year <- read_csv("~/Desktop/March/march_school_year.csv")
march_gender <- read_csv("~/Desktop/March/march_gender.csv")

my_postings <- read_csv("/Users/lt/Desktop/2025/my_employer_postings_and_applications_nov_to_feb17.csv") %>% 
mutate(job_id = as.factor(job_id),employer_name = as.factor(employer_name), industry = as.factor(industry), 
       max_salary = replace_na(max_salary, 0))


five_yrs <- last_5_years <- read_csv("~/Downloads/last 5 years.csv") %>% 
rename(date = "Postings Responded On Date") %>% 
 mutate(date = as.Date(date, "%m/%d/%Y"),
         year = year(date))



```

### March 2024

This analysis was to explore the top industries and applicants in March 2024. The first graph is a visualization of applicants by school year, including advanced degrees and alumni. The second graph visualizes the total applicants by gender.

```{r}
#| code-fold: true
#| cap-location: margin

sy_longer <- march_school_year |> 
  pivot_longer(
    cols = alumni:sophomore,
    names_to = "school_year",
    values_to = "applicants",
    values_drop_na = TRUE
  )

sy_longer |> 
  mutate(school_year = school_year |> fct_infreq() |> fct_rev()) |> 
  ggplot(aes(school_year, fill = school_year)) +
  geom_bar(show.legend = FALSE)+
  scale_color_brewer(palette = "Set1")+
  labs(
    x = "",
    y = "",
    title = "Number of Applicants by School Year",
    subtitle = "March 2024"
  )


march_longer <- march_gender |> 
  pivot_longer(
    cols = female:male,
    names_to = "gender",
    values_to = "applicants",
    values_drop_na = TRUE
  )

march_longer |> 
  drop_na(job_type) |> 
  mutate(job_type = job_type |> fct_rev()) |> 
  ggplot(aes(job_type, fill = gender)) +
  geom_bar(position = "dodge")+
  scale_color_brewer(palette = "Set1")+
  labs(x = "",
       y = "",
       fill = "Gender",
       title = "Applicants by Job Type and Gender", 
       subtitle = "March 2024")

```

### Applicants by Industry 
The following was completed to get a snapshot of student engagement during the end of the fall semester. 
```{r}
#| code-fold: true

applications <- my_postings 


applications |>
group_by(industry) |> 
  summarize(total = sum(applications_count)) |> 
  arrange(desc(total)) %>% 
  slice_head(n = 20) %>% 
  ungroup() %>% 
  mutate(industry = fct_reorder(industry, total)) %>% 
  ggplot(aes(industry, total, color = industry, size = total)) +
  geom_point() +
  coord_flip() +
  scale_y_continuous(labels = comma) +
  theme(legend.position = "none") +
  labs(x = "Industry",
       y = "Number of applicants",
       title = "Total Student Applicants by Industry",
       subtitle = "November 2024 to February 2025") 



```

### Employer Industries
This graph shows employer engagement by industry during the end of the fall semester. It reflects the number of job and internship postings by industry, versus student applications by industry as above. 

```{r}
#| code-fold: true

top_industries <- my_postings

top_industries %>% 
 count(industry, sort = TRUE) %>% 
  slice_head(n = 20) |> 
  mutate(industry = fct_reorder(industry, n)) |> 
  ggplot(aes(industry, n, fill = industry))+
  geom_col()+
  coord_flip()+
  theme(legend.position = "none")+
  labs(title = "Top Employer Industries",
       subtitle = "November 2024 to February 2025", 
       x = "Industry",
       y = "Postings count")

```

### Applications 2021-2024

Another snapshot to see the number of applicants from 2021 to 2024.
```{r}
#| code-fold: true

five_yrs %>% 
  filter(year != 2025 & !is.na(year)) %>% 
  group_by(year) %>% 
  summarize(total = sum(applications_count),
            n = n()) %>% 
  ggplot(aes(year,total)) +
  geom_line() +
  scale_y_continuous(labels = comma) +
  labs(x = "Year",
       y = "Applications",
       title = "Total Applications from 2021 to 2024")


```